ACARIS: Improving Conversational AI and Human Social Skills using User Embeddings

### 2023-05-23 paper.tex
progress done, baseline models established, now working purely on ACARIS

\subsection{Literature Review and Related Work}
\subsubsection{Studied Literature}
\begin{itemize}
	\item \textbf{Machine Learning with PyTorch and Scikit-Learn}\cite{raschka2022machine} by Yuxi Liu, Vahid Mirjalili, Sebastian Raschka
	\item \textbf{Hands-on Machine Learning with Scikit-Learn, Keras, and TensorFlow}\cite{geron2022hands} by Aurélien Géron
	\item \textbf{Transformers for Natural Language Processing}\cite{rothman2022transformers} by Denis Rothman, Antonio Gulli
\end{itemize}
\subsubsection{Related Work}
\begin{itemize}
	\item \textbf{Human-AI Collaboration Enables More Empathic Conversations in Text-based Peer-to-Peer Mental Health Support}\cite{sharma2022humanai}
	\item \textbf{Context Matters: Recovering Human Semantic Structure from Machine Learning Analysis of Large-Scale Text Corpora}\cite{https://doi.org/10.1111/cogs.13085}
\end{itemize}

@@

\subsection{Short Intro on Transformers}
The Transformer is a deep learning model proposed in 2017 by a team of Google Brain/Google Research researchers. It is mainly used in NLP, but it has also found its way into numerous vision projects (Latent Diffusion\cite{rombach2021highresolution}/Stable Diffusion/LLaVA\cite{liu2023visual}, to name a few).

@@

\section{Validation}
To validate our approach, we compared the performance of our model with the performance of a baseline model. We used the same model, DistilBERT, but without the user embeddings $e_u$. We fine-tuned both models on the same dataset and compared their performance on the same test set.
\section{Results}
NaN

>>>>

\subsection{Literature Review and Related Work}
\subsubsection{Studied Literature}
\begin{itemize}
	\item \textbf{Machine Learning with PyTorch and Scikit-Learn}\cite{raschka2022machine} by Yuxi Liu, Vahid Mirjalili, Sebastian Raschka
	\item \textbf{Hands-on Machine Learning with Scikit-Learn, Keras, and TensorFlow}\cite{geron2022hands} by Aurélien Géron
	\item \textbf{Transformers for Natural Language Processing}\cite{rothman2022transformers} by Denis Rothman, Antonio Gulli
	\item 
\end{itemize}
\subsubsection{Related Work}
\begin{itemize}
	\item \textbf{Human-AI Collaboration Enables More Empathic Conversations in Text-based Peer-to-Peer Mental Health Support}\cite{sharma2022humanai}
	\item \textbf{Context Matters: Recovering Human Semantic Structure from Machine Learning Analysis of Large-Scale Text Corpora}\cite{https://doi.org/10.1111/cogs.13085}
\end{itemize}

@@

\subsection{Short Intro on Transformers}
The Transformer is a deep learning model architecture proposed in 2017 by a team of Google Brain/Google Research researchers. It is mainly used in NLP, but it has also found its way into numerous vision projects (Latent Diffusion\cite{rombach2021highresolution}/Stable Diffusion/LLaVA\cite{liu2023visual}, to name a few). The architecture aims to replace RNNs by using attentions mechanisms (self-attention, in particular) and positional encodings to model long-term dependencies in sequential data.

@@

\section{Validation}
To validate our approach, we compared the performance of our model to the performance of a baseline model. We used the same model, DistilBERT, but without the user embeddings $e_u$. We fine-tuned both models on the same dataset and compared their performance on the same test set. The base model performed as follows (mean scores over 5 training runs):
\begin{itemize} %%% (1/5)
	\item \textbf{Accuracy} $\approx$ 0.95
	\item \textbf{Precision\textsubscript{\textnormal{mean of all three scores}}} = 0.93
	\item \textbf{Recall\textsubscript{\textnormal{mean of all three scores}}} = 0.93
	\item \textbf{F1\textsubscript{\textnormal{mean of all three scores}}} $\approx$ 0.93
\end{itemize}
The model with user embeddings $e_u$ performed as follows (mean scores over 5 training runs):
\begin{itemize}
	\item \textbf{Accuracy} $\approx$ 0.97
	\item \textbf{Precision\textsubscript{\textnormal{mean of all three scores}}} = NaN
	\item \textbf{Recall\textsubscript{\textnormal{mean of all three scores}}} = NaN
	\item \textbf{F1\textsubscript{\textnormal{mean of all three scores}}} $\approx$ NaN
\end{itemize}
\section{Results}
NaN
